Additional analysis

### 2019-03-10 README.Rmd
Add correct instructions

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below. 
Title <- "The effect of NGO crackdowns on individual philanthropy"
```

@@

### Abstract

@@

This repository contains the data and code for our paper:

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to cite

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to download or install

You can download the compendium as a zip from from this URL: </archive/master.zip>

Or you can install this compendium as an R package, testingthing, from GitHub with:

```r
pkgbuild::compile_dll()
```

### Licenses

@@

### Contributions

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below. 
Title <- "The effect of NGO crackdowns on individual philanthropy"
Authors <- "Suparna Chaudhry and Andrew Heiss"
Year <- "2019"
```

@@

## Abstract

@@

This repository contains the data and code for our paper. Our pre-print is online here:

> `r Authors`. (`r Year`). *`r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <https://doi.org/xxx/xxx>

## How to cite

@@

> `r Authors`. (`r format(Sys.Date(), "%Y")`). *Compendium of R code and data for `r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <https://doi.org/xxx/xxx>

## How to download and install

You can either [download the compendium as a ZIP file](/archive/master.zip) or use GitHub to clone or fork the compendium repository (see the green "Clone or download" button at the top of the GitHub page).

In order to reproduce this project, you'll need to install the compendium as an R package. After downloading the compendium, do the following:

1. Open the compendium as a project in RStudio (double click on `crackdownsphilanthropy.proj`).
2. Install the **pkgbuild**, **devtools**, **rstan**, and **rstantools** packages, either with RStudio's "Packages" panel or by running `install.packages(c("pkgbuild", "devtools", "rstan", "rstantools"))`
3. Due to [strange](https://github.com/stan-dev/rstantools/issues/52) [incompatibilties](https://github.com/klutometis/roxygen/issues/822#issuecomment-441425591) with **roxygen2** and **rstantools**, you need to compile the Stan C++ binary DLLs before building the actual **crackdownsphilanthropy** compendium package. Run `pkgbuild::compile_dll()` and wait a few minutes while the Stan models are built.
4. Finally, build the compendium package by clicking on the "Install and Restart" button in RStudio's "Build" panel.

You should now be able to run `library(crackdownsphilanthropy)` and reproduce all the findings in the paper (as well as the paper itself).

To reproduce the analysis, run `make build` from RStudio's "Terminal" panel. Open `analysis/_site/` to see the results. Run `make serve` to serve the site at <http://localhost:7000>.

To repdocuce the paper, run `make html` or `make tex` or `make docx` or `make paper` (for all three output formats) from the terminal. Open `manuscript/` (or `manuscript/tex_out/` for PDFs) to see the results.

## Licenses

@@

## Contributions
